A tutorial of Solving the defined integral problem with OpenMp

### 2023-06-09 documentation/article01/article.tex
Beginning a new article

	\par Let $x = [a,b]$ and $n=partitions+1=points$ of $[a,b]$ than it is true to say that $x_0 = a < x_1 < ... < x_{n-1} < x_n = b$. Being the interval between two points $\Delta_{x_k} = x_k - x_{k-1}$ than the equation \ref*{eq:secondApproximation} can be rewrote as in the equation \ref{eq:genericApproximation}.\newline

>>>>

	\par Let $x = [a,b]$ and $n=partitions+1=points$ of $[a,b]$ than it is true to say that $x_0 = a < x_1 < ... < x_{n-1} < x_n = b$. Being the interval between two points $\Delta_{x_k} = x_k - x_{k-1}$ than the equation \ref*{eq:secondApproximation} can be rewrote as the equation \ref{eq:genericApproximation}.\newline
